Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-23 ms.tex
I re-arranged the figures and Tables so they occur closer to their descriptions in the text.

Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
{\bf [Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here. For {\shb}, 
brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak.
These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}. We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.

@@

@@

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations}\label{tab:obsParam}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including the reset times and overheads. The FWHM is the measured median value of the time series around 1.6$\mu$m.}
\end{deluxetable*}

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.

>>>>

Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
{\bf [Adam, Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here. For {\shb}, 
brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak.
These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}. We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.

@@

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including the reset times and overheads. The FWHM is the measured median value of the time series around 1.6$\mu$m.}
\end{deluxetable*}

@@

@@

Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.
